High resolution, annual maps of field boundaries for smallholder-dominated croplands at national scales

### 2021-10-08 inst/manuscript/manuscript.Rmd
EarthArxiv statement added back

>>>>

note: This pre-print is a revised version of a manuscript that has undergone one round of peer review in \emph{Frontiers in Artificial Intelligence}, where it has been resubmitted. This version will be updated as it is further revised, and the final published version will be accessible through its DOI link.

### 2021-10-08 inst/manuscript/manuscript.tex
EarthArxiv statement added back

\begin{document}
%%Edited by @jhollist 09/15/2014
%%Adds title from YAML
\begin{singlespace}
\begin{center}
\huge High resolution, annual maps of field boundaries for
smallholder-dominated croplands at national scales
\end{center}
%%Adds subtitle from YAML
%%Adds Author, correspond email asterisk, and affilnum from YAML
\begin{center}
\large
%% removed space here
Lyndon D. Estes\textsuperscript{*} \textsuperscript{1}, 
%% removed space here
Su Ye \textsuperscript{1,2}, 
%% removed space here
Lei Song \textsuperscript{1}, 
%% removed space here
Boka Luo \textsuperscript{1,3}, 
%% removed space here
J. Ronald Eastman \textsuperscript{1,3}, 
%% removed space here
Zhenhua Meng \textsuperscript{1}, 
%% removed space here
Qi Zhang \textsuperscript{1}, 
%% removed space here
Dennis McRitchie \textsuperscript{4}, 
%% removed space here
Stephanie R. Debats \textsuperscript{4}, 
%% removed space here
Justus Muhando \textsuperscript{5}, 
%% removed space here
Angeline H. Amukoa \textsuperscript{5}, 
%% removed space here
Brian W. Kaloo \textsuperscript{5}, 
%% removed space here
Jackson Makuru \textsuperscript{5}, 
%% removed space here
Ben K. Mbatia \textsuperscript{5}, 
%% removed space here
Isaac M. Muasa \textsuperscript{5}, 
%% removed space here
Julius Mucha \textsuperscript{5}, 
%% removed space here
Adelide M. Mugami \textsuperscript{5}, 
%% removed space here
Judith M. Mugami \textsuperscript{5}, 
%% removed space here
Francis W. Muinde \textsuperscript{5}, 
%% removed space here
Fredrick M. Mwawaza \textsuperscript{5}, 
%% removed space here
Jeff Ochieng \textsuperscript{5}, 
%% removed space here
Charles J. Oduol \textsuperscript{5}, 
%% removed space here
Purent Oduor \textsuperscript{5}, 
%% removed space here
Thuo Wanjiku \textsuperscript{5}, 
%% removed space here
Joseph G. Wanyoike \textsuperscript{5}, 
%% removed space here
Ryan B. Avery \textsuperscript{6}, 
%% removed space here
Kelly K. Caylor \textsuperscript{6,7,8}, 
\end{center}
%%Adds affiliations from YAML
\begin{justify}
% \footnotesize \emph{
% \\*
\footnotesize\textsuperscript{1}Graduate School of Geography, Clark
University, Worcester, MA, USA\\\\*
% \\*
\footnotesize\textsuperscript{2}Department of Natural Resources and the
Environment, University of Connecticut, Storrs, CT, USA\\\\*
% \\*
\footnotesize\textsuperscript{3}Clark Labs, Clark University, Worcester,
MA, USA\\\\*
% \\*
\footnotesize\textsuperscript{4}Independent contributor\\\\*
% \\*
\footnotesize\textsuperscript{5}SpatialCollective, Nairobi, Kenya\\\\*
% \\*
\footnotesize\textsuperscript{6}Department of Geography, University of
California Santa Barbara, Santa Barbara, CA, USA\\\\*
% \\*
\footnotesize\textsuperscript{7}Earth Research Institute, University of
California Santa Barbara, Santa Barbara, CA, USA\\\\*
% \\*
\footnotesize\textsuperscript{8}Bren School of Environmental Science and
Management, University of California Santa Barbara, Santa Barbara, CA,
USA\\\\*
% }
%%Adds corresponding author email(s) from YAML
\newcounter{num}
\setcounter{num}{1}
\\[0.1cm]
\footnotesize \emph{
\ifnum\value{num}=1%
\textsuperscript{*} corresponding author:
\fi
\href{mailto:lestes@clarku.edu}{\nolinkurl{lestes@clarku.edu}}
\stepcounter{num}
}
\end{justify}
%%Adds date from YAML
\normalsize

>>>>

\begin{document}
%%Edited by @jhollist 09/15/2014
%%Adds title from YAML
\begin{singlespace}
\begin{center}
\huge High resolution, annual maps of field boundaries for
smallholder-dominated croplands at national scales
\end{center}
%%Adds subtitle from YAML
%%Adds Author, correspond email asterisk, and affilnum from YAML
\begin{center}
\large
%% removed space here
Lyndon D. Estes\textsuperscript{*} \textsuperscript{1}, 
%% removed space here
Su Ye \textsuperscript{1,2}, 
%% removed space here
Lei Song \textsuperscript{1}, 
%% removed space here
Boka Luo \textsuperscript{1,3}, 
%% removed space here
J. Ronald Eastman \textsuperscript{1,3}, 
%% removed space here
Zhenhua Meng \textsuperscript{1}, 
%% removed space here
Qi Zhang \textsuperscript{1}, 
%% removed space here
Dennis McRitchie \textsuperscript{4}, 
%% removed space here
Stephanie R. Debats \textsuperscript{4}, 
%% removed space here
Justus Muhando \textsuperscript{5}, 
%% removed space here
Angeline H. Amukoa \textsuperscript{5}, 
%% removed space here
Brian W. Kaloo \textsuperscript{5}, 
%% removed space here
Jackson Makuru \textsuperscript{5}, 
%% removed space here
Ben K. Mbatia \textsuperscript{5}, 
%% removed space here
Isaac M. Muasa \textsuperscript{5}, 
%% removed space here
Julius Mucha \textsuperscript{5}, 
%% removed space here
Adelide M. Mugami \textsuperscript{5}, 
%% removed space here
Judith M. Mugami \textsuperscript{5}, 
%% removed space here
Francis W. Muinde \textsuperscript{5}, 
%% removed space here
Fredrick M. Mwawaza \textsuperscript{5}, 
%% removed space here
Jeff Ochieng \textsuperscript{5}, 
%% removed space here
Charles J. Oduol \textsuperscript{5}, 
%% removed space here
Purent Oduor \textsuperscript{5}, 
%% removed space here
Thuo Wanjiku \textsuperscript{5}, 
%% removed space here
Joseph G. Wanyoike \textsuperscript{5}, 
%% removed space here
Ryan B. Avery \textsuperscript{6}, 
%% removed space here
Kelly K. Caylor \textsuperscript{6,7,8}, 
\end{center}
%%Adds affiliations from YAML
\begin{justify}
% \footnotesize \emph{
% \\*
\footnotesize\textsuperscript{1}Graduate School of Geography, Clark
University, Worcester, MA, USA\\\\*
% \\*
\footnotesize\textsuperscript{2}Department of Natural Resources and the
Environment, University of Connecticut, Storrs, CT, USA\\\\*
% \\*
\footnotesize\textsuperscript{3}Clark Labs, Clark University, Worcester,
MA, USA\\\\*
% \\*
\footnotesize\textsuperscript{4}Independent contributor\\\\*
% \\*
\footnotesize\textsuperscript{5}SpatialCollective, Nairobi, Kenya\\\\*
% \\*
\footnotesize\textsuperscript{6}Department of Geography, University of
California Santa Barbara, Santa Barbara, CA, USA\\\\*
% \\*
\footnotesize\textsuperscript{7}Earth Research Institute, University of
California Santa Barbara, Santa Barbara, CA, USA\\\\*
% \\*
\footnotesize\textsuperscript{8}Bren School of Environmental Science and
Management, University of California Santa Barbara, Santa Barbara, CA,
USA\\\\*
% }
%%Adds corresponding author email(s) from YAML
\newcounter{num}
\setcounter{num}{1}
\\[0.1cm]
\footnotesize \emph{
\ifnum\value{num}=1%
\textsuperscript{*} corresponding author:
\fi
\href{mailto:lestes@clarku.edu}{\nolinkurl{lestes@clarku.edu}}
\stepcounter{num}
}

%\begin{center}
This pre-print is a revised version of a manuscript that has undergone
one round of peer review in \emph{Frontiers in Artificial Intelligence},
where it has been resubmitted. This version will be updated as it is
further revised, and the final published version will be accessible
through its DOI link.
%\end{center}

\end{justify}
%%Adds date from YAML
\normalsize
